---
title: "reshaping_data"
author: "promitosh"
date: "7/24/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```
str(murders)
class(murders)
length("pop")
x<-murders$population
data("murders")
library(dslabs)
install.packages("tidyverse")
data("murders")
head("murders")
str("murders")
data("gapminder")tidy_data %>%
ggplot(aes(year, fertility, color = country)) +
geom_point()
tidy_data %>%
ggplot(aes(year, fertility, color = country)) +
geom_point()


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```
tidy_data %>%
ggplot(aes(year, fertility, color = country)) +library(ggplot)
tidy_data<-gapminder %>%
filter(country %in% c("South Korea","Germany")) %>%
select(country,year,fertility)
head(tidy_data)
tidy_data %>%
ggplot(aes(year,fertility,color=country))
geom_point()
tidy_data %>%
+ ggplot(aes(year,fertility,color=country)) geom_point()
tidy_data %>%
+ ggplot(aes(year,fertility,color=country))geom_poin
tidy_data %>%
ggplot(aes(year, fertility, color = country)) +
geom_point()
path <- system.file("extdata", package="dslabs")
filename <- file.path(path,  "fertility-two-countries-example.csv")
wide_data<-read_csv(filename)
library(tidyverse)
wide_data<-read_csv(filename)
new_tidy_data <- wide_data %>%
gather(year, fertility, `1960`:`2015`)
new_tidy_data
class(new_tidy_data$year)
class(new_tidy_data$year)
class(tidy_data)
new_tidy_data <- wide_data %>%gather(year, fertility,-country,convert=TRUE)
library(dplyr)
new_tidy_data <- wide_data %>%
gather(year, fertility,-country,convert=TRUE)
library(dslabs)
library(ggplot)
library(ggplot2)
new_tidy_data <- wide_data %>%
gather(year, fertility,-country,convert=TRUE)
library(tidyverse)
library(dplyr)
data("gapminder")
new_tidy_data <- wide_data %>% gather(year, fertility,-country,convert=TRUE)
new_tidy_data
new_tidy_data %>%
ggplot(aes(year,fertility,color=country))
geom_point()
new_tidy_data %>% ggplot(aes(year,fertility,color=country))
geom_point()
new_tidy_data %>%
ggplot(aes(year,fertility,color=country))
new_tidy_data %>% ggplot(aes(year,fertility,color=country))
new_tidy_data %>% ggplot(aes(year,fertility,color=country))geom_point()
geom_point()
new_tidy_data %>% ggplot(aes(year,fertility,color=country))geom_point()
new_tidy_data %>% + ggplot(aes(year,fertility,color=country)) + geom_point()
new_tidy_data %>%ggplot(aes(year,fertility,color=country))
geom_point()
geom_point(new_tidy_data)
new_tidy_data %>%
ggplot(aes(year, fertility, color = country)) +
geom_point()
new_wide_data <- new_tidy_data %>% spread(year, fertility)
select(new_wide_data, country, `1960`:`1967`)
dat<-raw_data %>% gather(key,value,-country)
path <- system.file("extdata", package = "dslabs")
filename <- file.path(path, "life-expectancy-and-fertility-two-countries-example.csv")
raw_# split on all underscores, pad empty cells with NA
dat %>% separate(key, c("year", "first_variable_name", "second_variable_name"), 
fill# split on first underscore but keep life_expectancy merged
dat %>% separate(key, c("year", "variable_name"), sep = "_", extra = "merge")
fill = "right")
dat <- read_csv(filename)



geom_point()
# gather wide data to make new tidy data
getwd()
library(dslabs)
getwd()
a<-1
b<-1
c<- -1
x<-(-b+sqrt(b^2-4*a*c))/(2*a)
str(murders)
class(murders)
length("pop")
x<-murders$population
data("murders")
library(dslabs)
install.packages("tidyverse")
data("murders")
head("murders")
str("murders")
data("gapminder")
data(gapminder)
data("gapminder")
library(dslabs)
install.packages("tidyverse")
library(dplyr)
data("gapminder")
str(gapminder)
library(ggplot2)
library(ggplot)
tidy_data<-gapminder %>%
filter(country %in% c("South Korea","Germany")) %>%
select(country,year,fertility)
head(tidy_data)
tidy_data %>%
ggplot(aes(year,fertility,color=country))
geom_point()
tidy_data %>%
+ ggplot(aes(year,fertility,color=country)) geom_point()
tidy_data %>%
+ ggplot(aes(year,fertility,color=country))geom_poin
tidy_data %>%
ggplot(aes(year, fertility, color = country)) +
geom_point()
path <- system.file("extdata", package="dslabs")
filename <- file.path(path,  "fertility-two-countries-example.csv")
wide_data<-read_csv(filename)
library(tidyverse)
wide_data<-read_csv(filename)
new_tidy_data <- wide_data %>%
gather(year, fertility, `1960`:`2015`)
new_tidy_data
class(new_tidy_data$year)
class(new_tidy_data$year)
class(tidy_data)
new_tidy_data <- wide_data %>%gather(year, fertility,-country,convert=TRUE)
library(dplyr)
new_tidy_data <- wide_data %>%
gather(year, fertility,-country,convert=TRUE)
library(dslabs)
library(ggplot)
library(ggplot2)
new_tidy_data <- wide_data %>%
gather(year, fertility,-country,convert=TRUE)
library(tidyverse)
library(dplyr)
data("gapminder")
new_tidy_data <- wide_data %>% gather(year, fertility,-country,convert=TRUE)
new_tidy_data
new_tidy_data %>%
ggplot(aes(year,fertility,color=country))
geom_point()
new_tidy_data %>% ggplot(aes(year,fertility,color=country))
geom_point()
new_tidy_data %>%
ggplot(aes(year,fertility,color=country))
new_tidy_data %>% ggplot(aes(year,fertility,color=country))
new_tidy_data %>% ggplot(aes(year,fertility,color=country))geom_point()
geom_point()
new_tidy_data %>% ggplot(aes(year,fertility,color=country))geom_point()
new_tidy_data %>% + ggplot(aes(year,fertility,color=country)) + geom_point()
new_tidy_data %>%ggplot(aes(year,fertility,color=country))
geom_point()
geom_point(new_tidy_data)
new_tidy_data %>%
ggplot(aes(year, fertility, color = country)) +
geom_point()
new_wide_data <- new_tidy_data %>% spread(year, fertility)
select(new_wide_data, country, `1960`:`1967`)
dat<-raw_data %>% gather(key,value,-country)
path <- system.file("extdata", package = "dslabs")
filename <- file.path(path, "life-expectancy-and-fertility-two-countries-example.csv")
raw_dat <- read_csv(filename)
dat <- raw_dat %>% gather(key, value, -country)
head(dat)
dat$key[1:5]
dat %>% separate(key, c("year", "variable_name"))
dat %>% separate(key, c("year", "first_variable_name", "second_variable_name"),
fill = "right")
dat %>% separate(key, c("year", "variable_name"), sep = "_", extra = "merge")
dat %>% separate(key, c("year", "variable_name"), sep = "_", extra = "merge") %>%
spread(variable_name, value)
dat %>%
separate(key, c("year", "first_variable_name", "second_variable_name"), fill = "right") %>%
unite(variable_name, first_variable_name, second_variable_name, sep="_")
dat %>%
separate(key, c("year", "first_variable_name", "second_variable_name"), fill = "right") %>%
unite(variable_name, first_variable_name, second_variable_name, sep="_") %>%
spread(variable_name, value) %>%
rename(fertility = fertility_NA)
d <- read_csv("C:\Users\User\Desktop\times.csv")
d <- read_csv("C:\\Users\\User\\Desktop\\times.csv")
d
tidy_data <- d %>%
gather(time, `2015`:`2017`)
tidy_data <- d %>% gather(time, `2015`:`2017`)
tidy_data <- d %>% gather(year, time, `2015`:`2017`)
tidy_data
tidy_data <- d %>% gather(age_group, year, time, `2015`:`2017`)
tidy_data <- d %>% gather(age, time, `2015`:`2017`)
tidy_data
spread_data<-tidy_data %>% spread(year, time)
tidy_data <- d %>% gather(year, time, `2015`:`2017`)
spread_data<-tidy_data %>% spread(year, time)
spread_data
head(stat)
head(stats)
library(tidyverse)
library(dslabs)
str(co2)
c02
data(co2)
class(CO2)
data("co2")
data("CO2")
class(co2)
str(co2)
str(CO2)
co2
head(co2)
co2_wide <- data.frame(matrix(co2, ncol = 12, byrow = TRUE)) %>%
setNames(1:12) %>%
mutate(year = as.character(1959:1997))
co2_tidy
co2_tidy <- gather(co2_wide,month,co2,-year)
head(co2_tidy)
co2_wide <- data.frame(matrix(co2, ncol = 12, byrow = TRUE)) %>%
setNames(1:12) %>%
mutate(year = as.character(1959:1997))
library(deplyr)
library(dslabs)
install.packages(deplyr)
library(deplyr)
co2_wide <- data.frame(matrix(co2, ncol = 12, byrow = TRUE)) %>%
setNames(1:12) %>%
mutate(year = as.character(1959:1997))
library(tidyverse)
co2_wide <- data.frame(matrix(co2, ncol = 12, byrow = TRUE)) %>%
setNames(1:12) %>%
mutate(year = as.character(1959:1997))
head(co2_wide)
co2_tidy <- gather(co2_wide,month,co2,-year)
head(co2_tidy)
str(co2_tidy)
co2_tidy <- gather(co2_wide,month,co2)
head(co2_tidy)
str(co2_wide)
co2_tidy <- gather(month,co2,-year)
names(co2_wide)
co2_tidy <- gather(co2_wide,month,co2,-year)
head(co2_tidy)
co2_tidy[44:47]
co2_tidy[3:5]
co2_wide[3:5]
co2_tidy %>% ggplot(aes(as.numeric(month), co2, color = year)) + geom_line()
class(month)
type(month)
library(dslabs)
data(admissions)
dat <- admissions %>% select(-applicants)
head(dat)
dat_tidy <- spread(dat, gender, admitted)
head(dat)
head(dat_tidy)
tmp <- gather(admissions, key, value, admitted:applicants)
tmp
tmp2 <- unite(tmp, column_name, c(key, gender))
head(tmp)
tmp2 <- unite(tmp, column_name, c(gender, key))
head(tmp2)
tmp2 <- unite(tmp, column_name, c(key, gender))
tmp2


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
