---
title: "string parsing"
author: "promitosh"
date: "8/2/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
commas <- function(x) any(str_detect(x, ","))
murders_raw %>% summarize_all(commas)
#>   state population total murder_rate
#> 1 FALSE       TRUE  TRUE       FALSE

data %>% mutate_at(2:3, funs(str_replace_all(., c("\\$|,"), ""))) %>% 
    mutate_at(2:3, as.numeric)
    
library(stringr)
s
x<-'22"'
x
x<-"5\'6\""
cat(x)
murders_raw$population[1:3]
commas <- function(x) any(str_detect(x, ","))
murders_raw %>% summarize_all(commas)
test_1 <- str_replace_all(murders_raw$population, ",", "")
test_1 <- as.numeric(test_1)
test_2 <- parse_number(murders_raw$population)
identical(test_1, test_2)
murders_new <- murders_raw %>% mutate_at(2:3, parse_number)
head(murders_new)
murders_new%>% head()
cat(` LeBron James is 6'8" `)
cat<-` LeBron James is 6'8" `
x<-` LeBron James is 6'8" `
x<-"LeBron James is 6’8\" "
cat(x)
murders_raw$population[1:3]
test_1 <- str_replace_all(murders_raw$population, ",", "")
head(test_1)
test_1 %>% mutate_at(1:3, as.numeric)
test_1 <- as.numeric(test_1)
data <- data.frame(A = c(1,2,3,4),
B = c(2,3,4,1),
C = c(4,1,9,0))
data
data %>% mutate_all(parse_number)
parse_number(data)
parse_number(test_1)
cal<-data.frame(Month=c(jan,feb,mar),sales=c($111,$220,$555))
cal<-(Month=c(jan,feb,mar),sales=c($111,$220,$555))
data %>% mutate_at(2:3, as.numeric)
data <- data.frame(A = c(1,2,3,4), B = c("2,00",3,4,1),C = c(4,1,9,0))
data
data %>% mutate_at(2:3, as.numeric)
dat %>% mutate_at(2:3, funs(str_replace_all(., c("\\$|,"), ""))) %>%
mutate_at(2:3, as.numeric)
data %>% mutate_at(2:3, funs(str_replace_all(., c("\\$|,"), ""))) %>%
mutate_at(2:3, as.numeric)
data %>% mutate_at(2:3, parse_number)
data <- data.frame(A = c(1,2,3,4), B = c("2,00",3,4,1),C = c(4,1,9,0))
data %>% mutate_at(2:3, parse_number)

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
