---
title: "wevscraping"
author: "promitosh"
date: "7/30/2020"
output: word_document
---
For the guacamole recipe page, we already have done this and determined that we need the following selectors:
h <- read_html("http://www.foodnetwork.com/recipes/alton-brown/guacamole-recipe-1940609")
recipe <- h %>% html_node(".o-AssetTitle__a-HeadlineText") %>% html_text()
prep_time <- h %>% html_node(".m-RecipeInfo__a-Description--Total") %>% html_text()
ingredients <- h %>% html_nodes(".o-Ingredients__a-Ingredient") %>% html_text()
 create a list
 guacamole <- list(recipe, prep_time, ingredients)
 
 Since recipe pages from this website follow this general layout, we can use this code to create a function that extracts this information
 get_recipe <- function(url){
    h <- read_html(url)
    recipe <- h %>% html_node(".o-AssetTitle__a-HeadlineText") %>% html_text()
    prep_time <- h %>% html_node(".m-RecipeInfo__a-Description--Total") %>% html_text()
    ingredients <- h %>% html_nodes(".o-Ingredients__a-Ingredient") %>% html_text()
    return(list(recipe = recipe, prep_time = prep_time, ingredients = ingredients))
} 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
library(tidyverse)
library(rvest)
h <- read_html(url)
library(rvest)
url <- "https://en.wikipedia.org/wiki/Murder_in_the_United_States_by_state"
h <- read_html(url)
h<- read_html("http://www.foodnetwork.com/recipes/alton-brown/guacamole-recipe-1940609")
h <- read_html(url)
url <- "https://en.wikipedia.org/wiki/Murder_in_the_United_States_by_state"
h <- read_html(url)
get_recipe("http://www.foodnetwork.com/recipes/food-network-kitchen/pancakes-recipe-1913844")
 the functions html_form(), set_values(), and submit_form() permit to query a webpage from R. 
We learned that tables in html are associated with the table node.
list of objects class xml_node
The html_nodes() function returns a list of objects of class xml_node. We can see the content of each one using, for example, the html_text() function. You can see the content for an arbitrarily picked component like this
If the content of this object is an html table, we can use the html_table() function to convert it to a data frame:
h<-read_html(url)
library(tidyverse)
library(rvest)
h <- read_html(url)
library(rvest)
url <- "https://en.wikipedia.org/wiki/Murder_in_the_United_States_by_state"
h <- read_html(url)
class(h)
h<- read_html("http://www.foodnetwork.com/recipes/alton-brown/guacamole-recipe-1940609")
library(rvest)
url <- "https://en.wikipedia.org/wiki/Murder_in_the_United_States_by_state"
h<- read_html("http://www.foodnetwork.com/recipes/alton-brown/guacamole-recipe-1940609")
ingredients <- h %>% html_nodes(".o-Ingredients__a-Ingredient")%>% html_text()
recipe <- h %>% html_node(".o-AssetTitle__a-HeadlineText")%>% html_text()

guacamole <- list(recipe, prep_time, ingredients)
prep_time <- h %>% html_node(".m-RecipeInfo__a-Description--Total") %>% html_text()

h<- read_html("http://www.foodnetwork.com/recipes/alton-brown/guacamole-recipe-1940609")

ingredients <- h %>% html_nodes(".o-Ingredients__a-Ingredient")%>% html_text()
recipe <- h %>% html_node(".o-AssetTitle__a-HeadlineText")%>% html_text()
prep_time <- h %>% html_node(".m-RecipeInfo__a-Description--Total") %>% html_text()

guacamole <- list(recipe, prep_time, ingredients)

get_recipe <- function(url)
{
h <- read_html(url)
recipe <- h %>% html_node(".o-AssetTitle__a-HeadlineText") %>% html_text()
prep_time <- h %>% html_node(".m-RecipeInfo__a-Description--Total") %>% html_text()
ingredients <- h %>% html_nodes(".o-Ingredients__a-Ingredient") %>% html_text()
return(list(recipe = recipe, prep_time = prep_time, ingredients = ingredients))
}

get_recipe("http://www.foodnetwork.com/recipes/food-network-kitchen/pancakes-recipe-1913844")
url<-"https://web.archive.org/web/20181024132313/http://www.stevetheump.com/Payrolls.htm"
h <- read_html(url)
nodes <- html_nodes(h, "table")
html_table(nodes[[8]])
data("nodes")
nodes<-html_nodes(h,"table")
nodes<-html_table(nodes[[2]])
nodes<-html_table(nodes[[1]])
tab3<-nodes<-html_table(nodes[[3]])
tab3<-html_table(nodes[[3]])
tab1<-nodes<-html_table(nodes[[1]])
tab4<-nodes<-html_table(nodes[[4]])
nodes<-html_nodes(h,"table")
tab4<-nodes<-html_table(nodes[[4]])
tab_1<-nodes<-html_table(nodes[[10]])
tab_1<-html_table(nodes[10])

url<- "https://web.archive.org/web/20181024132313/http://www.stevetheump.com/Payrolls.htm"
h<-read_html(url)
nodes<-html_nodes(h,"table")
tab_1<-html_table(nodes[10])
tab_1 <- as.data.frame(tab_1)
tab_1 <- tab_1[-1, -1]
names(tab_1) <- c("Team", "Payroll", "Average")

tab_2<-html_table(nodes[19])
tab_2 <- as.data.frame(tab_2)
head(tab_2)
tab_2<-html_table(nodes[19])
tab_2 <- as.data.frame(tab_2)
head(tab_2)
tab_2<-tab_2[-1,]

names(tab_2) <- c("Team", "Payroll", "Average")
str(tab_1)
str(tab_2)

full_join(tab_1,tab_2, by = "Team") %>%
nrow()

url<- "https://en.wikipedia.org/w/index.php?title=Opinion_polling_for_the_United_Kingdom_European_Union_membership_referendum&oldid=896735054"
h<-read_html(url)
tab<-html_nodes(h,"table")
length(tab)
length(tab)

tab[[5]] %>% html_table(fill = TRUE) %>%
names()


## R Markdown



When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```



## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
